Accuracy and stability for elliptic operators in a finite volume context

### 2023-05-24 example/EBCM/hoeb_petsc/_doc/paper.tex
I believe that this document clearly defines how the next angel will enter the dance on our particular pinhead

We are solving Poisson's equation for field $\psi$, given charge $\rho$:
\begin{equation}
  \nabla \cdot (\nabla \psi) = \rho
  \label{eqn::poisson}
\end{equation}
If we integrate equation \ref{eqn::poisson} and apply the divergence theorem 
over control volumes we get
\begin{equation}
\int_{V_\ibold} \nabla \cdot (\nabla \psi ) dV = \int_{\partial
  V_\ibold} \nabla \psi\cdot \nhat  dA = \int_{V_\ibold} \rho dV
\end{equation}
Without approximation, we can say that the surface integral can be
computed by a sum over the faces that comprise the surface of the
volume.
\begin{equation}
\sum_{f: f \in \partial V_\ibold} \nabla \psi \cdot \nhat dA = \int_{V_\ibold} \rho dV
\end{equation}
Using equations \ref{eqn::faceavg} and \ref{eqn::volavg}, this becomes 
\begin{equation}
\sum_{f: f \in \partial V_\ibold} \avg{\nabla \psi \cdot \nhat}_f A_f
= \avg{\rho}_\ibold V_\ibold
\label{eqn::discretePoisson}
\end{equation}
A finite volume operator is defined by the algorithm to compute the
integral of fluxes at each face.  We have three types of face, open
faces (the faces between two volumes that are aligned with coordinate
directions), domain faces, and cut faces.  For now, let's say we have
homogeneous Neumann boundary conditions at domain and cut faces
$\nabla \psi \cdot \nhat = 0 |\partial \Omega$.  In this case, to
describe the algorithm, we need only describe how to compute $<\nabla
\psi \cdot \nhat>$ on open faces.

@@

All volumes and faces  start with an  index $\ibold \in Z^D$.
We start from face $\fbold$.   Say we want to get
the distance from $\fbold$ with index $\ibold$ to a volume $V_1$
with index $\vbold$.  The distance $D_\fbold(V_1)$ is given by
the Manhattan disance:
\begin{equation}
  D_\fbold{V_1) = \sum\limits_{d \in {1...D}} |\vbold^d - \ibold_0^d|.
\label{eqn::uptownFunk}
\end{equation}
$\gbold_\fbold(V_1)$, the weight of the $V_1$ equation in $\fbold$ system
is given by
\begin{equation}
  \gbold_\fbold(V_1))  \equiv \frac{1}{D\fbold(\V1)^{P_w})},
\label{eqn::weightFunk}  
\end{equation}
where we call $P_w$ the weighting exponent.
The weighting matrix $W_\fbold = \{\{\wbold_{i,j}\}\}$ is diagonal
\begin{equation}
w_{i,j} =
\left(
\begin{array}{l}
 \gbold_\fbold(V_i) \mbox{ if } $(i==j)$)
 0  \mbox{otherwise}}
\end{array}
\right)
$$
Once one has the Taylor coefficients, she can compute the flux through
the open face using  equation \ref{eqn::faceavg}.   Put into matrix
form, we define  vector  $Q_\fbold = \{q^p_\fbold\}$:
$$
q^p_\fbold = p^d \mcal^{p-e^d}_\fbold
$$
and the flux at the face is given by
$$
<\nabla \psi>_\fbold = Q C P= Q ((WM)^T(WM))^{-1} (WM)^T  P.
$$
One would like to avoid inverting $A$ every time one withes to apply
an elliptic operator at a point.  Since everything in sight is a
linear operator, we can simply say that there must exist an equivalent
operator $S$ such that
$$
(S P)_\fbold = <\nabla \psi>_\fbold = Q C= (Q ((WM)^T(WM))^{-1} (WM)^T  P)_\fbold.
$$
Since this has to work for all $\psi$, we can define the stencil as
$$
 S_\fbold = Q C = (Q ((WM)^T(WM))^{-1} (WM)^T  )_\fbold = Q A^{-1} WM^T.
 $$

>>>>

We are solving Poisson's equation for field $\psi$, given charge $\rho$:
\begin{equation}
  \nabla \cdot (\nabla \psi) = \rho
  \label{eqn::poisson}
\end{equation}
If we integrate equation \ref{eqn::poisson} and apply the divergence theorem 
over control volumes we get
\begin{equation}
\int_{V_\ibold} \nabla \cdot (\nabla \psi ) dV = \int_{\partial
  V_\ibold} \nabla \psi\cdot \nhat  dA = \int_{V_\ibold} \rho dV
\end{equation}
Without approximation, we can say that the surface integral can be
computed by a sum over the faces that comprise the surface of the
volume.
\begin{equation}
\sum_{f: f \in \partial V_\ibold} \nabla \psi \cdot \nhat dA = \int_{V_\ibold} \rho dV
\end{equation}
Using equations \ref{eqn::faceavg} and \ref{eqn::volavg}, this becomes 
\begin{equation}
\sum_{f: f \in \partial V_\ibold} \avg{\nabla \psi \cdot \nhat}_f A_f
= \avg{\rho}_\ibold V_\ibold
\label{eqn::discretePoisson}
\end{equation}
A finite volume operator is defined by the algorithm to compute the
integral of fluxes at each face.  We have three types of face, open
faces (the faces between two volumes that are aligned with coordinate
directions), domain faces, and cut faces.  For now, let's say we have
homogeneous Neumann boundary conditions at domain and cut faces
$\nabla \psi \cdot \nhat = 0 |\partial \Omega$.  In this case, to
describe the algorithm, we need only describe how to compute 
$<\nabla\psi \cdot \nhat>$ on open faces.

@@

All volumes and faces  start with an  index $\ibold \in Z^D$.
We start from face $\fbold$.   Say we want to get
the distance from $\fbold$ with index $\ibold$ to a volume $V_1$
with index $\vbold$.  The distance $D_\fbold(V_1)$ is given by
the Manhattan disance:
\begin{equation}
  D_\fbold(V_1) = \sum\limits_{0 <= d < D} |\vbold^d - \ibold_0^d|.
\label{eqn::uptownFunk}
\end{equation}
$\gbold_\fbold(V_1)$, the weight of the $V_1$ equation in $\fbold$ system
is given by
\begin{equation}
  \gbold_\fbold(V_1)  \equiv \left(\frac{1}{D_\fbold(V_1) } \right)^{P_w},
\label{eqn::weightFunk}  
\end{equation}
where we call $P_w$ the weighting exponent.
The weighting matrix $W_\fbold = \{\{\wbold_{i,j}\}\}$ is diagonal
\begin{equation}
w_{i,j} =
\left(
\begin{array}{ll}
 \gbold_\fbold(V_i) & \mbox{ if } $(i==j)$ \\
 0   & \mbox{ otherwise }
\end{array}
\right)
\end{equation}
Once one has the Taylor coefficients, she can compute the flux through
the open face using  equation \ref{eqn::faceavg}.   Put into matrix
form, we define  vector  $Q_\fbold = \{q^p_\fbold\}$:
\begin{equation}
q^p_\fbold = p^d \mcal^{p-e^d}_\fbold
\end{equation}
and the flux at the face is given by
\begin{equation}
<\nabla \psi>_\fbold = Q C P= Q ((WM)^T(WM))^{-1} (WM)^T  P.
\end{equation}

\subsection{Stencil formulation}
One would like to avoid inverting $A$ every time she wishes to apply
an elliptic operator at a point.  Since everything in sight is a
linear operator, we can simply say that there must exist an equivalent
operator $S$ such that
\begin{equation}
(S P)_\fbold = <\nabla \psi>_\fbold = Q C= (Q ((WM)^T(WM))^{-1} (WM)^T  P)_\fbold.
\end{equation}
Since this has to work for all $\psi$, we can define the stencil as
\begin{equation}
 S_\fbold = Q C = (Q ((WM)^T(WM))^{-1} (WM)^T  )_\fbold = Q A^{-1} WM^T.
\end{equation}
